---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.


16. Yuqoridagi masalaga yana bitta qo'shimcha qilamiz. Endi qaysi qavatda joylashganidan tashqari, chap, usha qavatda nechinchi honadonligini chiqaring (1,2,3)
```text
30 honadondan iborat 10 qavatli binoga hush kelibsiz
Honadon raqamini kiriting: 6
6-honadon 2-qavatda bo'lib, o'ngdan chapga sanaganda 3-uy
```
```text
30 honadondan iborat 10 qavatli binoga hush kelibsiz
Honadon raqamini kiriting: 4
4-honadon 2-qavatda bo'lib, chapdan sanaganda 1-uy
```
